%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Nuclear Physics B}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Proyecto: Caracterizaci\'on y clasificaci\'on de series de tiempo con redes neuronales}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{Valery Alejandra G\'omez Escamilla}

\address{}

\begin{abstract}
Se busca caracterizar series de tiempo por medio de la herramienta RStudio con el fin de clasificar los clientes que una empresa posee. Por medio de redes neuronales se clasifican los clientes, en base a la forma de consumo en un producto determinado. Se utiliza el criterio de tendencia de las series para la clasificación, así mismo se concluyen la cantidad de tipos de clientes diferentes que cuenta la empresa, y se sub clasifican en modo más específico.
%% Text of abstract

\end{abstract}

\begin{keyword}

  series de tiempo \sep redes neuronales \sep clasificaci\'on \sep caracterizaci\'on.
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introducción}
Uno de los problemas más clásicos en la vida cotidiana es la predicción de comportamiento de fenómenos, así como la anticipación de sucesos. De manera formal todo fenómeno que tiene ocurrencia en un lapso o por un periodo de tiempo determinado se puede tratar de resolver y modelar mediante el uso de series de tiempo. 
De forma puntual se abordan las series de tiempo con características e interpretación muy específica, es decir esta herramienta funciona con los supuestos que serán mencionados en antecedentes. Tenemos una empresa que se dedica a la venta unitaria de productos, y se desea conocer los tipos de cientes que se poseen con el fin de clasificarlos para la implementación de estrategias de recuperación, es decir, me interesa conocer si un cliente es propenso a abandonarme respecto al comportamiento que sus últimas compras me refleja, e incluso conocer cuales de mis clientes de forma general presentan una demanda a la alza es decir que desde su primer compra a la actual se han dedicado a comprar más.
\section{Antecedentes}

\section{Trabajo relacionado}
\section{Solución propuesta}

\section{Evaluación}

\section{Conclusiones}

\section{Referencias}
%\label{}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{00}

%% \bibitem{label}
%% Text of bibliographic item

%\bibitem{}

\end{thebibliography}

\thanks{Este trabajo fue realizado en la asignatura de Simulación de Sistemas de la Maestría en Ciencias de Ingeniería de Sistemas, de la Facultad de Ingeniería Mecánica y Eléctrica de la Universidad Autónoma de Nuevo León bajo la dirección de la Dra. S. Elisa Schaeffer}

\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.
